Geometric variational problems

### 2020-11-12 NSF2020/Description/preliminarywork.tex
RJR going through prelim work

\begin{figure}[!]
\begin{center}
\includegraphics[width=1\textwidth]{figures/PW_fig1A-D.pdf}
\includegraphics[width=1\textwidth]{figures/PW_fig1E-H.pdf}
\end{center}\vspace{-0.3in}
\caption{\footnotesize (A) A vesicle formed by amphiphilic particles in
  shear flow, and the tank-treading motion (B)--(D). The separation of
  particle pairs in (B) and (C) illustrate inter-leaflet slip.  (E)--(G)
  Tank-treading reaches a steady state in elliptical aspect ratio,
  major-axis angle, and circumference.}
\label{fig:tanktreading}
\end{figure}
\section{Preliminary Work on Two-dimensional Vesicle Hydrodynamics in Shear Flow\label{sec:preliminary_work}} 
%\section{Preliminary work on elastic moduli}
To derive a bending modulus, we first considered a planar bilayer subject to a uniform vertical load on the particle centers (Figure \ref{fig:bend}). 
Using a clamped condition at one end, the restoring force in the free part of the bilayer opposes the load.
For small deformations, it is possible to solve the bilayer loading in closed form, and 
this analytical solution (red curve) basically overlaps the midplane of the particle based solution (Figure \ref{fig:bend}A).
We thereby derived a bending modulus $\KB$ in the range 8.51 -- 13.54 \kBT. Throughout the proposal, \kBT\; = 4.11$\times 10^{-21}$ J.
Experimental measurements have accurately determined the bending modulus for several lipid types, with 
typical values lying around 10 \kBT\; \cite{Naetal15,VeBrPa15,NAGLE2000159,PhysRevLett.113.248102}.

@@

Our preliminary work is encouraging because in all cases, the bending, stretch, and tilt elastic moduli for the collection of amphiphiles
were in excellent agreement with the experimental values. This fact is especially remarkable 
since we assigned the main model parameters $\rho$ and $\gamma$ reasonable physical values, rather than using them as tuning parameter. 
Nevertheless, the characterization of material properties is incomplete. For one, the preliminary simulations involved relatively low particle numbers (20 to 30), and so we still need to
perform convergence studies with large particle-number systems to arrive at conclusive results. Secondly, we have yet to establish a functional
relationship between the model parameters and elastic moduli. Finally, to have relevance in physics and biology
we must incorporate the remaining twist and saddle splay deformations.
The following simulation outline shows how will achieve aims.

>>>>

\begin{figure}[!]
\begin{center}
\includegraphics[width=1\textwidth]{figures/PW_fig1A-D.pdf}
\includegraphics[width=1\textwidth]{figures/PW_fig1E-H.pdf}
\end{center}
\vspace{-0.3in}
\caption{\label{fig:tanktreading}\footnotesize (A) A vesicle formed by
  amphiphilic particles in shear flow, and the tank-treading motion
  (B)--(D). The separation of particle pairs in (B) and (C) illustrate
  inter-leaflet slip.  (E)--(G) Tank-treading reaches a steady state in
  elliptical aspect ratio, major-axis angle, and circumference.}
\end{figure}
\section{Preliminary Work on Elasticity and Two-dimensional Vesicle Hydrodynamics in Shear Flow}
\label{sec:preliminary_work}
The motivation for Specific Aims 1-3
stemmed from the successful of demonstration, gradient driven
self-assembly of amphiphilic particles into two-dimensional micelles,
bilayer membranes, \cite{Fu2018_SIAM}, and recreation of the vesicles tank-treading phenomenon
under a new coarse-grained description.

Our preliminary work on membrane elasticity 
is particulary encouraging because the effective bending, stretch, and tilt elastic moduli we calculated
for collections of amphiphile were in excellent agreement with the experimental values.
The initial success is underscored by the fact we assigned reasonable physical values to 
the main model parameters of the HAP energy, rather than tuning parameter.

To derive a bending modulus, we first considered a planar bilayer subject to a uniform vertical load on the particle centers (Figure \ref{fig:bend}). 
Using a clamped condition at one end, the restoring force in the free part of the bilayer opposes the load.
For small deformations, it is possible to solve the bilayer loading in closed form, and 
this analytical solution (red curve) basically overlaps the midplane of the particle based solution (Figure \ref{fig:bend}A).
We thereby derived a bending modulus $\KB$ in the range 8.51 -- 13.54 \kBT. Throughout the proposal, \kBT\; = 4.11$\times 10^{-21}$ J.
Experimental measurements have accurately determined the bending modulus for several lipid types, with 
typical values lying around 10 \kBT\; \cite{Naetal15,VeBrPa15,NAGLE2000159,PhysRevLett.113.248102}.

@@

Nevertheless, the characterization of material properties is incomplete. For one, the preliminary simulations involved relatively low particle numbers (20 to 30), and so we still need to
perform convergence studies with large particle-number systems to arrive at conclusive results. Secondly, we have yet to establish a functional
relationship between the model parameters and elastic moduli.
Finally, to have relevance in physics and biology we must incorporate the remaining twist and saddle splay deformations.
The following simulation outline shows how will achieve aims.
